---
title: "case_study"
author: "Ragyie Rawal"
date: "10/14/2021"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
```

## Load a dataset 

```{r}
data("nyc_airbnb")
```

## Questions to ask about this dataset: 
* How many rentals are there? Of what type? In what places? 
* Is price correlated with review score? 
* Which neighborhood is the most popular?
* Which neighborhood is the most expensive
* Which neighborhood has the highest reviews? 
* Is availability related to price?
* Is room type related to neighborhood? 
* Is the average length of stay related to borough? 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) 
```

Let's try to count things: 

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)

nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

Is room type related to neighbourhood?  

```{r}
nyc_airbnb %>% 
  janitor::tabyl(neighbourhood, room_type)

```

Let's look at price and room type...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() +
  facet_grid(. ~ room_type)
```

